Calendar-based graphics for visualising people's daily schedules

### 2017-07-09 main.Rmd
update code and upload the rda

This work was originally motivated by studying foot traffic in the city of Melbourne [@ped]. There have been 43 installed sensors counting pedestrians every hour across the downtown area until recently. The dataset can shed lights into understanding people's daily schedules, or assisting administration and business planning. Figure \ref{fig:facet-time} lends itself to a number of issues that make exploratory data visualisation challenging in many temporal-context applications involving human behaviours:

@@

```{r time-series-plot, fig.height = 4.5, fig.cap = "Time series plot about the number of pedestrians over the year of 2016 at two train stations in the city of Melbourne. Small multiples of line graphs demonstrate some common periodic behaviours, for example weekly patterns, possessed by both sensors."}
```

```{r facet-time, fig.cap = "Hourly pedestrian counts facetted by sensors and days of the week using lines. It features at least two types of seasons--time of day and day of week--at both stations primarily driven by the commuting traffic. There are much more weekenders around Flinders Street Station than Flagstaff Station."}
```

>>>>

This work was originally motivated by studying foot traffic in the city of Melbourne [@ped]. There have been 43 installed sensors counting pedestrians every hour across the downtown area until the end of 2016 (see Figure \ref{fig:ped-map}). The dataset can shed lights into understanding people's daily schedules, or assisting administration and business planning. To take a glimpse at such temporal-context data, we start with the conventional time series plot (Figure \ref{fig:time-series-plot}). Figure \ref{fig:facet-time} lends itself to a number of issues that make exploratory data visualisation challenging in many temporal-context applications involving human behaviours:

@@

```{r ped-map, fig.width = 4, out.width = "0.55\\linewidth", fig.cap = "Map of the Melbourne city along with purple dots indicating sensor locations."}
```

```{r time-series-plot, fig.height = 10.5, fig.cap = "Time series plot about the number of pedestrians over the year of 2016 at a selection of 7 sensors in the city of Melbourne. Coloured by the sensors, small multiples of lines show the foot traffic varies from one sensor to another in terms of both time and number. The traffic, specifically at two train stations (Flagstaff Station and Flinders Street Station), is primarily driven by the commuters, as depicted in the graph."}
```

```{r facet-time, fig.height = 10.5, fig.cap = "Hourly pedestrian counts facetted by sensors and days of the week using lines. It features at least two types of seasons--time of day and day of week--across all the sensors. The temporal patterns are subject to the sensor locations too."}
```

### 2017-07-09 main.tex
update code and upload the rda

This work was originally motivated by studying foot traffic in the city
of Melbourne \citep{ped}. There have been 43 installed sensors counting
pedestrians every hour across the downtown area until recently. The
dataset can shed lights into understanding people's daily schedules, or
assisting administration and business planning. Figure
\ref{fig:facet-time} lends itself to a number of issues that make
exploratory data visualisation challenging in many temporal-context
applications involving human behaviours:

@@

@@

\caption[Time series plot about the number of pedestrians over the year of 2016 at two train stations in the city of Melbourne]{Time series plot about the number of pedestrians over the year of 2016 at two train stations in the city of Melbourne. Small multiples of line graphs demonstrate some common periodic behaviours, for example weekly patterns, possessed by both sensors.}\label{fig:time-series-plot}
\end{figure}
\end{CodeChunk}

@@

\caption[Hourly pedestrian counts facetted by sensors and days of the week using lines]{Hourly pedestrian counts facetted by sensors and days of the week using lines. It features at least two types of seasons--time of day and day of week--at both stations primarily driven by the commuting traffic. There are much more weekenders around Flinders Street Station than Flagstaff Station.}\label{fig:facet-time}
\end{figure}
\end{CodeChunk}

>>>>

This work was originally motivated by studying foot traffic in the city
of Melbourne \citep{ped}. There have been 43 installed sensors counting
pedestrians every hour across the downtown area until the end of 2016
(see Figure \ref{fig:ped-map}). The dataset can shed lights into
understanding people's daily schedules, or assisting administration and
business planning. To take a glimpse at such temporal-context data, we
start with the conventional time series plot (Figure
\ref{fig:time-series-plot}). Figure \ref{fig:facet-time} lends itself to
a number of issues that make exploratory data visualisation challenging
in many temporal-context applications involving human behaviours:

@@

{\centering \includegraphics[width=0.55\linewidth]{figure/ped-map-1}

\caption[Map of the Melbourne city along with purple dots indicating sensor locations]{Map of the Melbourne city along with purple dots indicating sensor locations.}\label{fig:ped-map}
\end{figure}
\end{CodeChunk}

@@

\caption[Time series plot about the number of pedestrians over the year of 2016 at a selection of 7 sensors in the city of Melbourne]{Time series plot about the number of pedestrians over the year of 2016 at a selection of 7 sensors in the city of Melbourne. Coloured by the sensors, small multiples of lines show the foot traffic varies from one sensor to another in terms of both time and number. The traffic, specifically at two train stations (Flagstaff Station and Flinders Street Station), is primarily driven by the commuters, as depicted in the graph.}\label{fig:time-series-plot}
\end{figure}
\end{CodeChunk}

@@

\caption[Hourly pedestrian counts facetted by sensors and days of the week using lines]{Hourly pedestrian counts facetted by sensors and days of the week using lines. It features at least two types of seasons--time of day and day of week--across all the sensors. The temporal patterns are subject to the sensor locations too.}\label{fig:facet-time}
\end{figure}
\end{CodeChunk}
